---
title: "Donation Impact Simulated Experiment"
author: "Yanan Chen"
date: '2019-10-15'
output: rmarkdown::github_document
---

```{r}
set.seed(9079)
# the data for the group of students that receive persuaion 
dataW <- round(rnorm(316/2-13,30,1),2); print(dataW) 
# the data for the group of students that do not receive persuaion 
dataWO <- round(rnorm(316/2-24,20,1),2); print(dataWO) 
```

Analyse the (fabricated) data.
```{r}
#From the side by side boxplots we know there are suspected outliers for two data gorups.
boxplot(dataW,dataWO,names=c("with_persuasion","without_persuasion")) 
summary(dataW)
summary(dataWO)
```
In the boxplot of "with_persuasion", we can see the outlier is greater than Q3+1.5IQR=(30.72+1.5*(30.72-29.31))= 32.835, which is the data point 33.08.

In the boxplot of "without_persuasion", we can see the outliers are beyond the limit of (Q1-1.5IQR,Q3+1.5IQR)=(19.28-1.5*(20.57-19.28),20.57+1.5*(20.57-19.28))=(17.345, 22.505) the outliers are data points 16.79, 17.07, 22.99.

```{r}
#Hence, after removing these outliers we can get the final tables for these two data groups.
dataW_final <- sort(dataW[dataW<32.835])
dataWO_final <-sort(dataWO[17.345<dataWO]);dataWO_final <-sort(dataWO_final[dataWO_final<22.505])
#Tables for two data groups 
with_persuasion <- 1:length(dataW_final)
without_persuasion <- 1:length(dataWO_final)
# Table for the group that receives persuasion
table1 <-data.frame(with_persuasion,dataW_final);print(table1) 
# Table for the group that did not receive persuasion
table2 <- data.frame(without_persuasion,dataWO_final);print(table2) 

```

I then proceed to use the two sample t-test to check whether the mean of these two groups are different from each other.
The null hypothesis is that two groups have the same means on the average amount of money donation. 
```{r}
t.test(dataW_final,dataWO_final,var.equal = T,alternative="greater")

```

```{r}
# Assuming the synthetic data follow unknown distributiom, 
# I first intend to check normality using the shapiro.test()
# The null hypothesis is that the data is normal, the alternative hypothesis is the data is not normal.
shapiro.test(dataW_final)
shapiro.test(dataWO_final)
# Since we can see the p-values for these two data groups are both larger than 0.05,
#the null hypotheses cannot be rejected. Hence, the assumption of normality for two samples is satisfied.
```

```{r}
# Then I want to check whether the data have equal variances
var.test(dataW_final,dataWO_final)
```
Since we can see the p-value = 0.7153 larger than 0.05, the null hypotheses cannot be rejected. Hence, the assumption of equal variances for two samples is satisfied.

Conclusions 

With a p-value which is less than 2.2*10-16, we have strong evidence that the means of these two data groups are not equal. Therefore we reject the null hypothsis and conclude that the group that received persuasion that says their donation's impact will be matched is more likely to give more money compared to the group that received no persuasion.


